preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution

### 2021-05-30 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript_v1.Rmd
More WIP

In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE and other consortia have been profiled at relatively high resolution (10-300bp). The association of domain boundaries with CTCF and other architectural proteins [@rao20143d; @Tang:2015aa; @Phillips:2009aa] holds promise that these high-resolution marks may inform the more precise location of domain boundaries. Indeed, methods like Lollipop

>>>>

In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE [@ENCODE-Project-Consortium:2012aa] and other consortia have been profiled at relatively high resolution (10-300bp). The association of domain boundaries with CTCF and other architectural proteins [@rao20143d; @Tang:2015aa; @Phillips:2009aa] holds promise that these high-resolution marks may inform the more precise location of domain boundaries. Methods like Lollipop used

GM12878 (lympho-blastoid), K562 (chronic myelogenous leukemia)

Random forest has been used in multiple methods (Lollipop, 3dEpiLoop, Peakachu)

RAD21 signal was the most predictive feature, followed by CTCF (Lollipop)

Lollipop used motif strength, orientation, loop size, average sequence conservation, in-between features, gene expression.
